Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-09 ICML-submission/related-work.tex
Fix bibfiles

There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2007}.
In this problem, the learner is given a policy class $\Pi$, and
at each timestep $t$, an example $x_t$ is shown, with an associated cost vector $c_t$ hidden.
The learner then takes an action $\hat{y}_t$, and observed the incurred cost $c_t$.
The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
The online bandit multiclass learning problem is a special case of the contextual bandits problem,
where the cost $c_t(i)$ is the classification error $I(i \neq y_t)$,
and the policy class $\Pi$ is the set of linear classifiers
$\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
A series of works in the contextual bandits learning literature focus on
oracle-efficiency~\citep{DudikHKKLRZ11, Monster:2014, RakhlinS16, Syrgkanis2016a, Syrgkanis2016b}.
Specifically, they assume access to a policy optimization
oracle that receives a set of cost-sensitive learning examples and policy class $\Pi$,
return the policy in $\Pi$ that minimizes its empirical cost on the examples, and the algorithm
only call the oracle a polynomial number of times.
However, these algorithms are not truly computationally efficient in our setting,
as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{arora1997hardness}.

>>>>

The online bandit multiclass learning is a special case of the contextual bandits
problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
A series of works in the contextual bandits learning literature focuses on
oracle-efficiency, that is, they assume access to an
oracle that given a set of cost-sensitve learning examples,

There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2008}.
In this problem, the learner is given a policy class $\Pi$, and
at each timestep $t$, an example $x_t$ is shown, with an associated cost vector $c_t$ hidden.
The learner then takes an action $\hat{y}_t$, and observed the incurred cost $c_t$.
The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
The online bandit multiclass learning problem is a special case of the contextual bandits problem,
where the cost $c_t(i)$ is the classification error $I(i \neq y_t)$,
and the policy class $\Pi$ is the set of linear classifiers
$\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
A series of works in the contextual bandits learning literature focus on
oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014,
Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
Specifically, they assume access to a policy optimization
oracle that receives a set of cost-sensitive learning examples and policy class $\Pi$,
return the policy in $\Pi$ that minimizes its empirical cost on the examples, and the algorithm
only call the oracle a polynomial number of times.
However, these algorithms are not truly computationally efficient in our setting,
as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.
